Formatting Instructions \\for Authors Using \LaTeX{}

### 2016-05-28 doc/paper.tex
added a few adjectives:

RNN encoder-decoders are not the first corpus-based MT methodology (EBMT then SMT then this), and it is unlikely in this era of Big Data that they will be the last.
Focusing on corpus generation allows linguists to focus on capturing the most statistically prevalent linguistic phenomena, while insulating them from the strengths and weaknesses of various implementations.
For instance, EBMT suffers from relatively poor generalization and SMT has problems with nonlocality.
(RNN built on relatively shaky ground, since word vectors don't QUITE make sense for function words?)

@@

>>>>

RNN encoder-decoders are not the first corpus-based MT methodology (EBMT then SMT then this), and it is unlikely in this era of Big Data that they will be the last.
Focusing on corpus generation allows linguists to focus on capturing the most statistically prevalent linguistic phenomena, while insulating them from the strengths and weaknesses of various implementations.
For instance, EBMT suffers from relatively poor generalization and SMT has problems with nonlocality.
(RNN built on relatively shaky ground, since word vectors don't QUITE make sense for function words?)
Seems somewhat foolhardy to marginalize the domain experts
Significantly more engineering (man-hours?) seems to go into the machine-learning component.  (Well, granted, there are human translators who are spending many man-hours generating sentence pairs. But they're not intended for MT.)
Traditionally, corpus construction has been considered prohibitively expensive, ``scavenged'' from other sources like parliamentary proceedings or lecture subtitles.
But must this be so? Vast untapped resource of students or whatever.

@@

Return of the linguist: it is relatively easy to come up with examples that industrial-grade systems fail. (hmm,)
he was shown the car
他 给 展示 了 车?

\section{Single-Line Scoring}

It is a testament to how indisidious these errors can be that they persisted this long (tst2010 was distributed as recently as IWSLT2015
This underscores the need for human post-editing, at the very least, for test sets.
In a shared evaluation task with many language pairs, the most practical way for this is probably crowdsourcing.

It also demonstrates the tremendous imbalance between linguistic effort and machine learning effort/investment
